---
title: 'QMM #6'
output:
  pdf_document: default
  html_document: default
---

AP shipping company's problem formulation: 

// Objective function
min: 775x1 + 800x2 + 800x3 + 800x4 + 800x5 + 775x6 + 750x7;

// Constraints
Sunday number of workers  Constraint: x2 + x3 + x4 + x5 + x6 >= 18;
Monday number of workers Constraint: x3 + x4 + x5 + x6 + x7 >= 27;
Tuesday number of workers constraint: x1 + x4 + x5 + x6 + x7 >= 22;
Wednesday number of workers constraint: x1 + x2 + x5 + x6 + x7 >= 26;
Thursday number of workers constraint: x1 + x2 + x3 + x6 + x7 >= 25;
Friday number of workers constraint: x1 + x2 + x3 + x4 + x7 >= 21;
Saturday number of workers constraint: x1 + x2 + x3 + x4 + x5 >= 19;

integers x1, x2, x3, x4, x5 , x6, x7;

```{r}
library(lpSolveAPI)

y <- read.lp("Apshipping.lp")
y

solve(y) #Optimal solution found

```
What was the total cost? How many workers are available each day?
```{r}
get.objective(y)  #The minimum wage expense is $25,675

get.variables(y)  #Number of workers on Sunday is 19, Monday: 27,  Tuesday :24, Wednesday: 28, Thursday: 25, Friday: 24, Saturday: 20.

```



