---
title: 'QMM -Assignemnt #3'
output:
  html_document: default
  pdf_document: default
---


Heart is trying to minimize costs which includes shipping and production costs in both plant A and plant B. However, its supply is more than the demand and hence we need to creat a dummy destination, a warehouse in this case  to absorb the 10 units demand difference to reach the feasible solution. 

Objective function : Min(622 x11 + 614 x12 + 630 x13 + 641 x21 + x645 x22 + 649 x23)

Variables: x11 = number of AEDs produced and shipped from plant A to warehouse 1
x12=  number of AEDs produced and shipped from plant A to warehouse 2
x13=  number of AEDs produced and shipped from plant A to warehouse 3
x14= number of AEDs produced and shipped from plant A to dummy warehouse 4
x21=  number of AEDs produced and shipped from plant B to warehouse 1
x22 = number of AEDs produced and shipped from plant B to warehouse 2
x23=  number of AEDs produced and shipped from plant B to warehouse 3
x24=  number of AEDs produced and shipped from plant B to dummy warehouse 4


```{r}
library(lpSolveAPI)
x <- read.lp("Heart.lp")
x

```


Constraints:
Plant A capacity constraint:  x11 + x12 +x13 +x14 =100,
Plant B capacity constraint:  x21 +x22 +x23 +x24= 120,
Warehouse 1 Demand constraint:  x11+ x21 =80,
Warehouse 2 Demand Constraint:  x12 + x22 = 60,
Warehouse 3 Demand constraint:  x13 + x23 = 70,
Warehouse 4 Demand constraint: x14 + x24 =10

```{r}
solve(x)

get.objective(x)   #Total costs of shipping and production = $132790

get.variables(x)   #x11= 0, x12=60, x13=40 , x21= 80, x22= 0, x23= 30, x14, 0, x24 =10, total AEDs to be produced in Plant A= 100, and 110 in Plant B


```



